draft-data

### 2024-11-25 draftdata.Rmd
ypagenorespond

```{r clean, results='hide', hide =TRUE}
rm(list = ls())
```

@@

```{r package, hide=TRUE, results='hide'}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

@@

```{r functions 1, hide =TRUE, results='hide'}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

```{r functions 2, hide=TRUE, results='hide'}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

# Ego-Level Descriptives

@@

```{r sum gender, hide = TRUE, echo=FALSE }
summary(df_ego$gender)
```

@@

```{r counts gender-all, hide = TRUE, echo=FALSE }
table(df_ego$gender)
```

@@

```{r histogram gender, hide = TRUE, echo=FALSE }
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

```{r gender per dep., hide = TRUE, echo=FALSE }

@@

```{r summary h index, hide = TRUE, echo=FALSE }
summary(df_ego$h_index)
```

@@

```{r hist h index, hide = TRUE, echo=FALSE }
# Histogram of prestige scores for Wave 1

@@

```{r table per dep h index, hide = TRUE, echo=FALSE }
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

>>>>

```{r clean, echo=FALSE}
rm(list = ls())
```

@@

```{r package, echo=FALSE}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

@@

```{r functions 1, echo=FALSE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

```{r functions 2, echo=FALSE}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology"+"political science", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

@@

# Ego-Level Descriptives
Below you can find some descriptive information about the ego-level data after data preparation. For more information, consult the 'data preparation' part of this final report.

@@

```{r sum gender, echo=FALSE }
summary(df_ego$gender)
```

@@

```{r counts gender-all, echo=FALSE }
table(df_ego$gender)
```

@@

```{r histogram gender, echo=FALSE }
# Convert gender to a factor to avoid errors
df_ego$gender <- as.factor(df_ego$gender)
# Create the histogram with a dark theme and two colors for bars
ggplot(df_ego, aes(x = gender, fill = gender)) +
  geom_bar(color = "darkgrey", width = 0.6) +  # Add borders for bars
  scale_fill_manual(
    values = c("0" = "#FFFFB3", "1" = "#80B1D3"),  # Custom colors: yellow for females, blue for males
    labels = c("Female", "Male")  # Optional: customize legend labels
  ) +
  labs(
    title = "Gender Distribution",
    x = "Gender\n (0 = female, 1 = male)",
    y = "Count",
    fill = "Gender"  # Legend title
  ) +
  theme_minimal(base_family = "Arial") +  # Clean, minimal base theme
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark panel background
    panel.grid.major = element_line(color = "#444444"),  # Subtle grid lines
    panel.grid.minor = element_line(color = "#444444"),
    axis.text = element_text(color = "#f0f0f0"),  # White axis text
    axis.title = element_text(color = "#f0f0f0", face = "bold"),  # Bold white axis titles
    plot.title = element_text(color = "#f0f0f0", face = "bold", hjust = 0.5),  # White centered title
    legend.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark legend background
    legend.text = element_text(color = "#f0f0f0"),  # White legend text
    legend.title = element_text(color = "#f0f0f0")  # White legend title
    )

@@

```{r gender per dep., echo=FALSE }

@@

```{r summary h index, echo=FALSE }
summary(df_ego$h_index)
```

@@

```{r hist h index, echo=FALSE }
# Histogram of prestige scores for Wave 1

@@

```{r table per dep h index, echo=FALSE }
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```
